---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Travis build status](https://travis-ci.org/JayAchar/tbgeneratr.svg?branch=master)](https://travis-ci.org/JayAchar/tbgeneratr)

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/JayAchar/tbgeneratr?branch=master&svg=true)](https://ci.appveyor.com/project/JayAchar/tbgeneratr)

[![Coverage status](https://codecov.io/gh/JayAchar/tbgeneratr/branch/master/graph/badge.svg)](https://codecov.io/github/JayAchar/tbgeneratr?branch=master)

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
