---
title: "Generating admission variables"
author: "Jay Achar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Generating admission variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Introduction

The `tbgeneratr` package takes programmatic TB data cleaned using the `tbcleanr` package and generates additional variables. This vignette describes which variables can be calculated using only the cleaned admission data object. `tbgeneratr` has been developed for EpiInfo and Koch 6 data exports. It relies on standard variable naming by these software packages. 

# Workflow

``` {r adm-workflow}
library(tbcleanr)
library(tbgeneratr)

adm %>% 
  # clean imported admission data using tbcleanr
  tbcleanr::adm_data_cleanr() %>% 
  # generate adm variables using tbgeneratr
  tbgeneratr::adm_generator()
  
```

The `adm_generator()` function incorporates three functions - `age_generator()`, `bmi_generator()` and `start_splittr()`. These functions calculate the age in years at treatment start, the body mass index (BMI), and breaks apart the start treatment variable to alow easier grouping. 

# Additional arguments

``` {r adm-args}

adm %>%
  adm_generator(categorise = TRUE,
                paediatric = TRUE, 
                rm_orig = TRUE)

```

Three optional arguments can also be used with `adm_generator()`:

*  categorise - adds a factor variable `age_cat` splitting age in years into three categories;
*  paediatric - adds a factor varialbe `age_paeds` splitting age < 18 years into three additional categories;
*  rm_orig - removes variables used to generate the age and BMI variables. 

