---
title: "Getting Started"
author: "Jay Achar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Accessing instructions
This instruction vignette is available either online at **[Github](https://github.com/JayAchar/tbgeneratr)** or through **[emailing the author](mailto:jay.achar@london.msf.org?subject=tbgeneratr instructions)**. Alternatively, you may ask your medical manager since they may also have a copy. For the most up to date version, it's recommended to visit the online repository linked. 

# Purpose

This R package, `tbgeneratr`, has been developed to support MSF field staff using either Koch 6 or EpiInfo to augment the output from `tbcleanr`, a package designed to automate cleaning of routine TB programme data. The package will eventually fit into a workflow incorporating `tbcleanr` and `tbreportr`, a package being developed to generate standardised TB programme reports. 

# How to

To use this package, R experience is required. The R langugage must be downloaded and installed on the computer. This, and the download of the `tbgeneratr` package will require a functioning internet connection. 

This package accepts admission and laboratory data exported from Koch 6 or EpiInfo, then cleaned using `tbcleanr`. 

``` {r install}
require(devtools)
install_github("JayAchar/tbgeneratr")
library(tbgeneratr)
```

Aggregating functions have been developed to simplify multiple variable generation steps:

* `adm_generator` generates the age and BMI, in addition to splitting the start treatment date within the cleaned admission data frame. It is capable of working with data collected in Koch 6 and EpiInfo.
* `adm_lab_generator` generates baseline smear and culture status variables, with culture and smear conversion dates and baseline DST results. 

``` {r adm_generator}
adm <- adm_generator(adm, rm_orig = TRUE)

```

``` {r adm_lab_generator}
adm <- adm_lab_generator(adm, lab, baseline_days = 90)

```

Help files for individual functions are available in the usual way:
``` {r help}
?tbgeneratr::converter
```

# Future developments

Functionality will be added for adherance and change drug data sets. In parallel, `tbreportr` is being developed to automate cohort reporting for programme evaluation purposes and to monitor data quality within a programme.
